---
title: "Case Study"
author: "Andy Turner"
date: "2023-10-10"
output: html_document
---

## Getting in Data 

```{r}
library(p8105.datasets)
library(tidyverse)
library(ggridges)

data(nyc_airbnb)

nyc_airbnb= 
  nyc_airbnb |> 
  rename(borough= neighbourhood_group) |> 
  mutate(stars= review_scores_location / 2)

```

## Brainstorm Questions
- Where are AirBnBs expensive?
  - borough? neighborhood?
  - do other factors (room type) affect price? what about rating?
- How long are AirBnbs active?
  - Are AirBnbs illegal and do they get shut down?
- Which units have the most availability?
- How is review score impacted by location?
- How many apts are run by one host?
  - Does that affect price?
  - Does that vary by neighborhood?
- Where are AirBnBs?
  - Borough? Neighborhood?
  - Lat and long?
  
## Attempted Solutions
```{r}
nyc_airbnb |> 
  group_by(borough) |> 
  summarize(n_obs= n())
```
1 Bronx           649
2 Brooklyn      16810
3 Manhattan     19212
4 Queens         3821
5 Staten Island   261

```{r}
nyc_airbnb |> 
  group_by(neighbourhood) |> 
  summarize(n_obs= n())
```

```{r}
upper_prices_nyc =
  nyc_airbnb |> 
  mutate(price_rank= min_rank(desc(price))) |> 
  filter(price_rank < 10)

lower_prices_nyc =
  nyc_airbnb |> 
  mutate(price_rank= min_rank(price)) |> 
  filter(price_rank < 10)

upper_prices_nyc |> 
  group_by(borough) |> 
  summarize(n_obs= n())

lower_prices_nyc |> 
  group_by(borough) |> 
  summarize(n_obs=n())
```

## In Class Solutions
```{r}
nyc_airbnb |> 
  count(borough)

nyc_airbnb |> 
  group_by(borough) |> 
  summarize(mean_price= mean(price))

nyc_airbnb |> 
  group_by(borough, room_type) |> 
  summarize(mean_price= mean(price)) |> 
  pivot_wider(
    names_from = room_type,
    values_from= mean_price
  )

nyc_airbnb |> 
  group_by(borough, room_type) |> 
  summarize(median_price= median(price)) |> 
  pivot_wider(
    names_from = room_type,
    values_from= median_price
  )
```

```{r}
nyc_airbnb |> 
  ggplot(aes(x=price))+
  geom_histogram()+
  facet_grid(borough ~ room_type)
```

```{r}
nyc_airbnb |> 
  filter(price >= 9500)
```

```{r}
nyc_airbnb |> 
  filter(price <1000, room_type == "Entire home/apt") |> 
  ggplot(aes(x=price))+
  geom_histogram()+
  facet_grid(. ~ borough)
```

```{r}
nyc_airbnb |> 
  filter(price<1000, 
         room_type == "Entire home/apt",
         borough == "Manhattan") |> 
  group_by(neighbourhood) |> 
  summarize(
    n_apt = n(),
    mean_price= mean(price)) |> 
  arrange(desc(mean_price))

nyc_airbnb |> 
  filter(price<1000, 
         room_type == "Entire home/apt",
         borough == "Manhattan") |> 
  group_by(neighbourhood) |> 
  summarize(
    n_apt = n(),
    mean_price= mean(price)) |> 
  arrange(mean_price)
```

Arrange: helps you to sort the data you need
Summarize: helps display everything as well 
Group_by: Get things grouped to be easier to do data on

```{r}
nyc_airbnb |> 
  filter(
    price <1000,
    room_type == "Entire home/apt",
    borough == "Manhattan") |> 
  ggplot(aes(x=neighbourhood, y=price))+
  geom_boxplot(
  )

nyc_airbnb |> 
  filter(
    price <1000,
    room_type == "Entire home/apt",
    borough == "Manhattan") |> 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) |> 
  ggplot(aes(x=neighbourhood, y=price))+
  geom_boxplot(
  )

nyc_airbnb |> 
  filter(
    price <1000,
    room_type == "Entire home/apt",
    borough == "Manhattan") |> 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) |> 
  ggplot(aes(x=price, y=neighbourhood))+
  geom_density_ridges()
```

## Try to make a map
```{r}
nyc_airbnb |> 
  filter(
    price <1000,
    room_type == "Entire home/apt",
    borough == "Manhattan") |> 
  ggplot(aes(x=lat, y=long, color=price))+
  geom_point()
```

Try something else entirely --> teach data science website for leaflet
```{r}
library(leaflet)
nyc_airbnb |> 
  filter(
    price <1000,
    room_type == "Entire home/apt",
    borough == "Manhattan") |> 
  sample_n(500) |> 
  leaflet() |> 
  addTiles() |> 
  addMarkers(~lat, ~long)

library(leaflet)
nyc_airbnb |> 
  filter(
    price <1000,
    room_type == "Entire home/apt",
    borough == "Manhattan") |> 
  sample_n(1000) |> 
  leaflet() |> 
  addProviderTiles(providers$CartoDB.Positron) |> 
  addCircleMarkers(~lat, ~long, radius=0.5)
```